Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-15 write-ups/PLDI/paper.tex
Rewrite results description for responsiveness

\myfiglong\ref{fig:fine-grained-timing} reports the measure for three
configurations and represents the gather and execution time of the
non-cooperative kernel w.r.t. the quantity of workgroups allocated to
it. Times are in milliseconds, and a logarithmic scale is used since
gather times tend to be much smaller than execution times. The
horizontal grey lines indicates the desired rate for non-cooperative
kernels.

Responsiveness of the cooperative scheduling is measured by the gather
time. In all examples, we observe that the gather time grows as we ask
for more workgroups for the non-cooperative kernel: this is expected,
since the scheduler must wait for more workgroups to call $\offerkill$
or to reach a resizing barrier. Still, notice that the query barrier
leads to better and stable gather times for graph applications, since it
can collect all needed workgroups at the first time they pass through
the barrier. Gather time also application-dependent since it is related
to how often the cooperative kernel workgroups hit $\offerkill$ or
$\resizingglobalbarrier$.

>>>>

\myfiglong\ref{fig:fine-grained-timing} reports, on three
configurations, the gather and execution time of the non-cooperative
kernel w.r.t. the quantity of workgroups allocated to it. A logarithmic
scale is used for time since gather times tend to be much smaller than
execution times. The horizontal grey lines indicates the desired rate
for non-cooperative kernels.

Let's focus on the left figure which illustrates a work stealing
example: when the non-cooperative kernel is given only one workgroup, it
execution is so long that it cannot permit to terminate on time for a
screen refresh. The gather time is very good though, since the scheduler
only needs to collect one workgroup. As more workgroups are allocated to
the non-cooperative kernel, it can benefits from more computational
resources and thus lower its execution time: here the non-cooperative
kernel becomes fast enough with a quarter (resp. half) of available
workgroups for light (resp. heavy) graphics workload. Inversely, the
gather time augments since the scheduler must collect more and more
workgroups from the cooperative kernel.

On the middle and right figures, which depict graph algorithms, we find
again the same trend: as the number of workgroups allocated to the
non-cooperative task grows, the non-cooperative kernel execution time
lowers and the gather time raises. When the regular resizing barrier is
used, gather time can become quite long and exceed the execution time.
However, the scheduling responsiveness can benefits from the query
barrier: when this barrier is used, the gather time becomes almost
stable w.r.t. the number of workgroups that needs to be collected, since
the scheduler collects all needed workgroups as soon as they hit a
resizing barrier.
